Considering scale in multilayer animal social networks

### 2020-06-25 paper/manuscript.Rmd
intro edits

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales through ecological processes such as
trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into, for example, species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
In the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent. 
<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->

Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social associations
over long time periods 
represent shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales [e.g. @Piza_Roca_2018]. Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. We therefore define social scale as the explicit definition 
and measurement of social relationships [@Farine_2015a]. 
<!-- for QW:

@@

We examined scale-dependent multilayer networks motivated by behavioural, landscape, 
and spatial ecology to and applied this framework to caribou (*Rangifer
tarandus*) on Fogo Island, Newfoundland, Canada. We use study to
address two principal questions associated with scale-dependent multilayer
networks. First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? Second, can variation in the social, spatial,
and temporal scale improve our understanding of the relationship between 
social association and seasonal resource availability? We conclude with further 
development and application of scale in multilayer
networks with respect to habitat selection and space use, 
movement ecology and collective movement, and phenotypes and individual fitness.

>>>>

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales through ecological processes such as
trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
In the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent. 
<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->

Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social associations
over long time periods 
represent shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home
range overlap is an example of how animals share space over coarser spatial and
temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of social interactions, such as social association and home range overlap, vary
predictably [@Castles_2014; @Farine_2015a]. 
We therefore define social scale as the explicit definition 
and measurement of social relationships [@Farine_2015a]. 
<!-- for QW:

@@

We examined scale-dependent multilayer networks motivated by behavioural, landscape, 
and spatial ecology to and applied this framework to caribou (*Rangifer
tarandus*) on Fogo Island, Newfoundland, Canada. First, we test to what degree 
the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influences our ability to
interpret complex social systems. Second, we address how variation in the social, spatial,
and temporal scale improves our understanding of the relationship between 
social association and seasonal resource availability. We conclude with potential
future developments and applications of scale in multilayer
networks.
